---
title : "Tugas Besar FSD"
output : html_document
author : "Fakhri Ilham (18523060) & Muhammad Farhan (18523099)"
---

FACTOR ANALISYS


LANGKAH 1 :
Melakukan import dataset dengan menggunakan data prediksi FIFA 2018 Man of the Match
melakukan replacement nilai kolom NA menjadi 0 dengan fungsi is.na()
```{r}
#install.packages('psych')
library(psych)
myData <- read.csv("FIFA 2018 Statistics.csv")
fifa_results <- myData[,c(4:20, 22)]
fifa_results$X1st.Goal[is.na(fifa_results$X1st.Goal)] <- 0

head(fifa_results)
```

LANGKAH 2 :
Membuat matriks korelasi dan
Kaiser-Meyer-Olkin factor adequacy
```{r}
df_corr <- cor(fifa_results)
KMO(df_corr)
```

LANGKAH 3 :
MSA (measure of sampling adequacy) is a measure for exclusion of variables. If MSA < 0.5 the variable should be dropped. Variables with MSA > 0.6 are suitable, variables with MSA > 0.8 very well suited for factor analysis. The result tells us to drop "On.Target","Off.Target","Blocked", "Offsides", "Distance.Covered.Kms", "Yellow.Red", "Red", "first_goal" variables
```{r}
df1_fifaRes <- fifa_results[,c(1:3, 7, 9:12, 14:15, 17)]
head(df1_fifaRes)
```

LANGKAH 4 :
```{r}
library(corrplot)
df1_corr <- cor(df1_fifaRes) # Create a correlation matrix
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(round(df1_corr, 2), method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         diag=FALSE) # hide correlation coefficient on the principal diagonal
round(df1_corr, 2) # Correlation matrix in table form
```

LANGKAH 5 :
```{r}
library('GPArotation')
nfactors <- 4 # Based on the screeplot suggestion
nvars <- dim(df1_corr)[1]
factors <- fa(r = df1_corr, nfactors = nfactors, rotate = "Varimax")
factors
```

LANGKAH N :

```{r}
modelFA <- fa(r = factors, nfactors = 4, rotate = "varimax", fm="minres")
modelFA$loadings
```



LANGKAH N :
Melakukan visualisasi 
```{r}
load <- factors$loadings[,1:4] 
fa.diagram(factors, digits = 2)
```


LANGKAH N :
```{r}
plot(load, type="n")
text(load,labels=names(factors),cex=.7) 
```



```{r}
library('psy')
scree.plot(df1_corr)
```

```{r}
library(ggplot2)
# Plot Eigenvalues / Represented Variance
eigenvalues <- data.frame(factors$e.values)
colnames(eigenvalues) <- c("Values")
eigenvalues$Number <- 1:nrow(df1_corr)

eigenvalues$RepresentedVariance <- NA
for (i in 1:nrow(df1_corr)) {
    eigenvalues$RepresentedVariance[i] <- sum(eigenvalues$Values[1:i])/sum(eigenvalues$Values) * 
        100
}
eigenvalues$RepresentedVariance_text <- paste(round(eigenvalues$RepresentedVariance, 
    0), " %")

e1 <- ggplot(eigenvalues, aes(Number, y = Values), group = 1)
e1 <- e1 + geom_bar(stat = "identity")
e1 <- e1 + geom_line(aes(y = Values), group = 2)
e1 <- e1 + xlab("Number [-]")
e1 <- e1 + ylab("Eigenvalue [-]")
e1 <- e1 + geom_hline(aes(yintercept = 1), col = "red")
e1 <- e1 + geom_text(aes(label = RepresentedVariance_text), nudge_y = 0.2)
e1 <- e1 + ggtitle("Eigenvalues and explained Variance")
e1 <- e1 + theme_bw()
e1 <- e1 + scale_x_continuous(breaks = seq(1, 10, 1))
e1
```


